Response to Pachter’s Review

### 2020-01-23 index.Rmd
update

---
title: "Response to Pachter’s Review"
author: "Joshua Paik and Igor Rivin"
date: "1/22/2020"
output:
  pdf_document:
    keep_tex: yes
    toc: yes
  html_document:
    toc: yes
---

@@

Last Update: January 23rd 3:16 A.M. G.M.T.

>>>>

---
title: "Response to Pachter’s Review"
author: "Joshua Paik and Igor Rivin"
date: '1/22/2020, Last Update: 1/23/2020 3:16 A.M. G.M.T.'
output:
  pdf_document:
    keep_tex: yes
    toc: yes
  html_document:
    toc: yes
---

@@
